Comparing R packages for calculation of persistent homology

### 2020-03-19 tdabench-paper/tdabench.Rmd
updated parenthetical for consistency
added supplement ref to methods

Benchmark data was collected twice - once on a local machine and once on a remote computing node, each of which featured 16 GB random access memory.
Both datasets were compared for consistency and are publicly available at the repository linked below.
Data from the remote computing node is visualized in this report.
The larger point clouds required more than 16 GB of RAM to calculate persistent homology using a subset of the libraries; attempts to compute results resulted in runtime errors, and the corresponding output is missing from the corresponding figures and tables.
Fully reproducible code for all numerical results and figures can be found at https://github.com/eashwarsoma/TDA-benchmark.
Video explanations of TDA concepts and reproducing all results in this report can be found at https://tinyurl.com/TDABench.

@@

Large data and feature dimensionality often restricts persistent homology calculations to small point clouds due to computational limits.
When calculating persistent homology on a high-dimensional point cloud, as Vietoris-Rips feature dimension increases, there is a corresponding increase in runtime (Figure \ref{fig:box}).
Dionysus is clearly outmatched by GUDHI and Ripser as feature dimension increases, with the difference being clearest for larger point clouds; by feature dimension 5, Ripser outpaces GUDHI as well (Figure \ref{fig:box}).
It is unclear whether runtime for each library grows polynomially or exponentially (see Supplement).

>>>>

Benchmark data was collected twice - once on a local machine and once on a remote computing node, each of which featured 16 GB random access memory.
Both datasets were compared for consistency and are publicly available at the repository linked below.
Data from the remote computing node is visualized in this report.
The larger point clouds required more than 16 GB of RAM to calculate persistent homology using a subset of the libraries; attempts to compute results resulted in runtime errors, and the corresponding output is missing from the corresponding figures and tables.
Fully reproducible code for all numerical results and figures can be found at https://github.com/eashwarsoma/TDA-benchmark.
This GitHub repository also contains instructions for generating the Supplement referenced in this report's results.
Video explanations of TDA concepts and reproducing all results in this report can be found at https://tinyurl.com/TDABench.

@@

Large data and feature dimensionality often restricts persistent homology calculations to small point clouds due to computational limits.
When calculating persistent homology on a high-dimensional point cloud, as Vietoris-Rips feature dimension increases, there is a corresponding increase in runtime (Figure \ref{fig:box}).
Dionysus is clearly outmatched by GUDHI and Ripser as feature dimension increases, with the difference being clearest for larger point clouds; by feature dimension 5, Ripser outpaces GUDHI as well (Figure \ref{fig:box}).
It is unclear whether runtime for each library grows polynomially or exponentially (see Supplement for regression details).
